---
title: "README.Rmd Problem Set #7"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
library(dplyr)
library(tidyverse)
library(fivethirtyeight)
library(leaflet)
library(sf)
library(maps)

# USA specific data
library(USAboundaries)
library(tidycensus)
library(tmaptools)

USA_map <-  maps::map("state", plot = FALSE, fill = TRUE)
#plot(USA_map)

# Convert maps package map object to sf object using st_as_sf() again:
USA_sf <- USA_map %>% 
  st_as_sf(crs = 4326)

  
MA_sf <- USA_sf %>% 
filter(ID == "massachusetts")

#ggplot() +
  #geom_sf(data = MA_sf) 


MA_cities <- tibble(
  name = c("Boston", "Salem", "Worcester", "Springfield"), 
  lat = c(42.3601, 42.5195, 42.2626, 42.1015), 
  lon = c(-71.0589, -70.8967, -71.8023, -72.5898))

MA_cities_sf <- MA_cities %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326)
MA_cities

ggplot() +
  geom_sf(data = MA_sf) +
  geom_sf(data = MA_cities_sf, aes(col = name), size = 2) 

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
